\cvsection{Experience}

\begin{cventries}

  \cventry
    {Part-Time Software Engineer}
    {\href{https://www.commencis.com}{Commencis}}
    {Oct. 2022 - Present}
    {Istanbul, Turkey}
    {
      \begin{cvitems}
        \item {Currently working as a Part-Time Software Engineer}
      \end{cvitems}
    }

  \cventry
    {Software Engineer Intern}
    {\href{https://www.commencis.com}{Commencis}}
    {July 2022 - Sept. 2022}
    {Istanbul, Turkey}
    {
      \begin{cvitems}
        \item {Developed a garage sale web application that users can sell and buy items.}
        \item {Used React, Redux and TypeScript.}
        \item {Worked in Agile methodology with Commencis web development team and other teams.}
      \end{cvitems}
    }

  \cventry
    {Full-Stack Software Developer}
    {\href{https://lonca.co}{Lonca.co}}
    {April 2022 - Oct. 2022}
    {Delaware, USA}
    {
      \begin{cvitems}
        \item {Worked as a Full-Stack Developer at e-commerce start-up.}
        \item {Created new product entry and stock system.}
        \item {Built scheduled scrapers to extract new products and stocks from supplier websites.}
        \item {Developed back-end and front-end applications using Node.js, Express.js, MongoDB, AWS, Docker, React.js, Redux.}
      \end{cvitems}
    }

  \cventry
    {Data Science and Machine Learning Intern}
    {\href{https://www.eczacibasi.com.tr/en/home}{Eczacibasi}}
    {June 2022 - July 2022}
    {Istanbul, Turkey}
    {
      \begin{cvitems}
        \item {Analyzed and visualised data using Pandas, Numpy, Streamlit, Plotly libraries.}
        \item {Scraped data from web using Scrapy framework and stored it on MongoDB.}
        \item {Created a product recommendation engine for the customers based on their past transactions.}
        \item {Performed customer segmentation and basket analysis with past years data to optimize the profit.}
        \item {Developed an image recognition based machine learning project and trained ML models on Google Colab.}
      \end{cvitems}
    }

  \cventry
    {Undergraduate Research Assistant}
    {\href{https://iui.ku.edu.tr}{Intelligent User Interfaces Laboratory, Koc University}}
    {Feb. 2022 - June 2022}
    {Istanbul, Turkey}
    {
      \begin{cvitems}
        \item {Worked on AI-Assisted PowerPoint Designer Project under supervision of Dr. Metin Sezgin.}
        \item {Recognition of sketched shapes and creating a PowerPoint add-in solution.}
        \item {Developed a back-end server with Python Django framework.}
      \end{cvitems}
    }

  \cventry
    {Marketing Intern}
    {Influanza}
    {June 2017 - July 2017}
    {Berlin, Germany}
    {
      \begin{cvitems}
        \item {Influanza is an innovative social media marketing startup based in Istanbul.}
        \item {Made presentations on behalf of the brand at many events in the Berlin startup ecosystem, in order \\ for the brand to spread in the German market.}
      \end{cvitems}
    }

  %\cventry
  %  {Board Member}
  %  {Sporbi}
  %  {Nov. 2016 - June 2017}
  %  {Istanbul, Turkey}
  %  {
  %    \begin{cvitems}
  %      \item {Board member and content creator at start-up.}
  %      \item {Sport content website founded with a team in high school.}
  %    \end{cvitems}
  %  }

\end{cventries}
